### 2025-07-21 decision-making.qmd
20250721 - edits

Averaging projections from individuals tends to yield predictions that are more accurate than the accuracy of most forecasters in the group [@Mannes2014].
Indeed, when at least some of the projections bracket the truth, averaged predictions must be more accurate than the average individual forecaster—in terms of [mean absolute error](#sec-meanAbsoluteError) (MAE)—and averaged predictions are often much more accurate [@Larrick2024].
When referring to the accuracy of the "average individual forecaster", we are referring to accuracy in terms of [mean absolute error](#sec-meanAbsoluteError) (MAE)—not to the accuracy of the forecaster at the 50th percentile.
If none of the projections bracket the truth—e.g., all projections overestimate the truth—averaged predictions will be as accurate than the average individual forecaster in terms of [mean absolute error](#sec-meanAbsoluteError) [@Larrick2024].
In sum, "Averaging the answers of a crowd, therefore, ensures a level of accuracy no worse than the average member of the crowd and, in some cases, a level better than nearly all members" [@Larrick2024, p. 126].
Moreover, averaged projections tend to be more accurate than consensus-based judgments from groups of people that interact and discuss, due to cognitive biases associated with the social interaction among groups, such as herding in which people align their behavior with others [@Mannes2014; @Simoiu2019], though discussion can be helpful in some contexts [@Larrick2024].

@@

There is substantial [overconfidence](#sec-cognitiveBiasesOverconfidence) (in particular overestimation) in sports betting/gambling.
[A study](https://mattbrownecon.github.io/assets/papers/jmp/sportsbetting.pdf) (archived at <https://perma.cc/X2AW-SUBZ>) of frequent sports bettors found that they tended to predict that they would gain 0.3 cents for every dollar wagered, but in fact lost 7.5 cents for every dollar wagered [@Brown2025].
[Overconfidence](#sec-cognitiveBiasesOverconfidence) was greatest among those who frequently wagered multi-leg bets (parlays), losing ~25 cents for every dollar wagered [@Brown2025].

>>>>

Averaging projections from individuals tends to yield predictions that are more accurate than the accuracy of most forecasters in the group [@Mannes2014].
Indeed, when at least some of the projections bracket the truth, averaged predictions must be more accurate than the average individual forecaster—in terms of [mean absolute error](#sec-meanAbsoluteError) (MAE)—and averaged predictions are often much more accurate [@Larrick2024].
When referring to the accuracy of the "average individual forecaster", we are referring to accuracy in terms of [mean absolute error](#sec-meanAbsoluteError) (MAE)—not to the accuracy of the forecaster at the 50th percentile.
If none of the projections bracket the truth—e.g., all projections overestimate the truth—averaged predictions will be as accurate as the average individual forecaster in terms of [mean absolute error](#sec-meanAbsoluteError) [@Larrick2024].
In sum, "Averaging the answers of a crowd, therefore, ensures a level of accuracy no worse than the average member of the crowd and, in some cases, a level better than nearly all members" [@Larrick2024, p. 126].
Moreover, averaged projections tend to be more accurate than consensus-based judgments from groups of people that interact and discuss, due to cognitive biases associated with the social interaction among groups, such as herding in which people align their behavior with others [@Mannes2014; @Simoiu2019], though discussion can be helpful in some contexts [@Larrick2024].

@@

There is substantial [overconfidence](#sec-cognitiveBiasesOverconfidence) (in particular overestimation of one's actual performance) in sports betting/gambling.
[A study](https://mattbrownecon.github.io/assets/papers/jmp/sportsbetting.pdf) (archived at <https://perma.cc/X2AW-SUBZ>) of frequent sports bettors found that they tended to predict that they would gain 0.3 cents for every dollar wagered, but in fact lost 7.5 cents for every dollar wagered [@Brown2025].
[Overconfidence](#sec-cognitiveBiasesOverconfidence) was greatest among those who frequently wagered multi-leg bets (parlays), losing ~25 cents for every dollar wagered [@Brown2025].
